Network based multifactorial modelling microRNA-target interaction.

### 2019-10-15 NAR_form_article.Rmd
xps to eps conversion

\begin{figure*}[ht]
\begin{center}
\includegraphics[width=16cm,height=9cm]{Fig1.eps}
\end{center}
\caption{Schematic presentation of mechanism of network based model. 
    (\textbf{A}) In steady state, miRNAs (M: triangles) repress targets (G: circles) according to proportion of target expression level. 
    (\textbf{B}) Two fold increase in transcript level of Gene2 (G2) acts as a trigger (shown in red). 
    (\textbf{C}) Distribution of miRNA1 (M1) changes. 
    (\textbf{D)}) The change at expression of common target affects changes of proportional distribution of miRNA2 (M2). Expression values are rounded to integers for simplicity. Gray values on edges indicate initial distribution, red values indicate increase and blue values indicate decrease in distribution. Shades of circles indicate different levels of increase.}
\label{fig:fig1}
\end{figure*}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=9cm,height=17cm]{Fig2.eps}
\end{center}
\caption{Calculations to determine of miRNA binding and repression efficiency. $G$, Gene; $M$, miRNA; $STE$, seed type effect; $RE$, Region Effect; $E$, Energy; $STE^\prime$, normalized values of seed type efficiency coefficient; $RE^\prime$, normalized values of region efficiency coefficient; $E^\prime$, normalized values of energy coefficient. Numbering on edges match the pair order in Table \ref{tab:one} }
\label{fig:fig2}
\end{figure}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[width=15cm,height=8cm]{Fig3.eps}
\end{center}
\caption{Target regulations with interaction parameters. 
     (\textbf{A}) In the steady-state the repression activity of miRNAs on the targets after binding and repression efficiency. 
     (\textbf{B}) The changes the repression activities after increasing of G2 expression. 
     (\textbf{C}) Perturbation of primary neighborhoods of M1 miRNA (M1 miRNA group). 
     (\textbf{D}) Regulation of gene expression of other gene group via triggering target (common target between M1 and M2)}
\label{fig:fig3}
\end{figure*}

>>>>

\begin{figure*}[ht]
\begin{center}
\includegraphics[width=21cm,height=12cm]{fig1_new.eps}
\end{center}
\caption{Schematic presentation of mechanism of network based model. 
    (\textbf{A}) In steady state, miRNAs (M: triangles) repress targets (G: circles) according to proportion of target expression level. 
    (\textbf{B}) Two fold increase in transcript level of Gene2 (G2) acts as a trigger (shown in red). 
    (\textbf{C}) Distribution of miRNA1 (M1) changes. 
    (\textbf{D)}) The change at expression of common target affects changes of proportional distribution of miRNA2 (M2). Expression values are rounded to integers for simplicity. Gray values on edges indicate initial distribution, red values indicate increase and blue values indicate decrease in distribution. Shades of circles indicate different levels of increase.}
\label{fig:fig1}
\end{figure*}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=9cm,height=17cm]{fig2_new.eps}
\end{center}
\caption{Calculations to determine of miRNA binding and repression efficiency. $G$, Gene; $M$, miRNA; $STE$, seed type effect; $RE$, Region Effect; $E$, Energy; $STE^\prime$, normalized values of seed type efficiency coefficient; $RE^\prime$, normalized values of region efficiency coefficient; $E^\prime$, normalized values of energy coefficient. Numbering on edges match the pair order in Table \ref{tab:one} }
\label{fig:fig2}
\end{figure}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[width=15cm,height=8cm]{fig3_new.eps}
\end{center}
\caption{Target regulations with interaction parameters. 
     (\textbf{A}) In the steady-state the repression activity of miRNAs on the targets after binding and repression efficiency. 
     (\textbf{B}) The changes the repression activities after increasing of G2 expression. 
     (\textbf{C}) Perturbation of primary neighborhoods of M1 miRNA (M1 miRNA group). 
     (\textbf{D}) Regulation of gene expression of other gene group via triggering target (common target between M1 and M2)}
\label{fig:fig3}
\end{figure*}

### 2019-10-15 NAR_form_article.tex
xps to eps conversion

Apart from tools predicting miRNA:target pairs, there are databases that
provide experimentally validated miRNA:target interaction datasets. The
reliability in these datasets range from weak (e.g, western blot) to
strong (e.g, CLiP, CLASH). High-throughput methods ensure handling of
AGO (Argounate Protein) interacted miRNAs (CLiP) and their targets as
well (CLEAR-CLiP, CLASH). We constructed a large ceRNA network utilizing
high-throughput datasets containing chimeric reading of miRNA:target
pairs \citep{helwak_mapping_2013, moore_mirnatarget_2015} which expose
exact complementary seed regions.

@@

We have analysed the realistic network in context of perturbation
efficiencies of nodes. This process was run with 3 fold upregulation and
10 iteration in conditions where elements that have less than five
percent change are not taken into account (Codes are found at Section
6.5 in Supplementary Materials and Methods). With this approach,
SERPINE2 has been found as one of the most effective gene nodes in
network. We have observed that gaining steady-state in realistic network
takes a lot of time because of complex interactions, as expected, and
SERPINE2 exhibit highest efficiency at iteration 31 with given
conditions (see Section 6.6 in Supplementary Materials and Methos and
Figure S9 in Supplementary Figures). We ran the model with two fold of
iteration which is observed as most effective. We have observed that the
results of simulation with SERPINE2 gene, a serine protease inhibitor,
one of the overexpressed genes of breast cancer
\citep{yang2018expression, candia2006protease} is not convenient with
tumor tissue expression values, when we compared the tumor gene
expression dataset retrieved from TCGA and simulation results obtained
via our approach (see Section 6.6 in Supplementary Materials and
Methods). Simulation results were not expected to be consistent with
tumor tissue expression values because large number of abnormal
regulations were observed in these tissues. So, it might not said that a
single gene is responsible for entire regulations in cancer cells.
Besides, the all other factors such as up/down regulation of miRNAs or
other genes were ignored. Therefore, it would be more useful to test our
approach with an ideal dataset that includes entire informations of gene
expression values before and after the regulation of a known gene at
existing tissue, and miRNA expression values of this tissue at initial
conditions.

>>>>

Apart from tools predicting miRNA:target pairs, there are databases that
provide experimentally validated miRNA:target interaction datasets. The
reliability in these datasets range from weak (e.g, western blot) to
strong (.g, CLiP, CLASH). High-throughput methods ensure handling of AGO
(Argonaute Protein) interacted miRNAs (CLiP) and their targets as well
(CLEAR-CLiP, CLASH). We constructed a large ceRNA network utilizing
high-throughput datasets containing chimeric reading of miRNA:target
pairs \citep{helwak_mapping_2013, moore_mirnatarget_2015} which expose
exact complementary seed regions.

@@

We have analysed the realistic network in context of perturbation
efficiencies of nodes. This process was run with 3 fold upregulation and
10 iteration in conditions where elements that have less than five
percent change are not taken into account (Codes are found at Section
6.5 in Supplementary Materials and Methods). With this approach,
SERPINE2 has been found as one of the most effective gene nodes in
network. We have observed that gaining steady-state in realistic network
takes a lot of time because of complex interactions, as expected, and
SERPINE2 exhibit highest efficiency at iteration 31 with given
conditions (see Section 6.6 in Supplementary Materials and Methods and
Figure S9 in Supplementary Figures). We ran the model with two fold of
iteration which is observed as most effective. We have observed that the
results of simulation with SERPINE2 gene, a serine protease inhibitor,
one of the overexpressed genes of breast cancer
\citep{yang2018expression, candia2006protease} is not convenient with
tumor tissue expression values, when we compared the tumor gene
expression dataset retrieved from TCGA and simulation results obtained
via our approach (see Section 6.6 in Supplementary Materials and
Methods). Simulation results were not expected to be consistent with
tumor tissue expression values because large number of abnormal
regulations were observed in these tissues. So, it might not said that a
single gene is responsible for entire regulations in cancer cells.
Besides, the all other factors such as up/down regulation of miRNAs or
other genes were ignored. Therefore, it would be more useful to test our
approach with an ideal dataset that includes entire informations of gene
expression values before and after the regulation of a known gene at
existing tissue, and miRNA expression values of this tissue at initial
conditions.
